Using Genetic Algorithms to Find Approximations for the Minimum Vertex Cover Problem

### 2018-02-23 paper.tex
we're good
going to sleep

% including packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{hyperref}
\usepackage{hypcap}
\usepackage[autostyle]{csquotes}
\usepackage[]{biblatex}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage[end]{algpseudocode}

@@

\section{Experimental Results}
\label{sec:er}
For the experimental tests,
the genetic algorithm software package GENEsYs is used [1]misp.
This implementation is based on the widely used GENESIS software by Grefenstette
(see [3], pp. 374-377 misp), but allows for more 
flexibility concerning genetic operators and data monitoring.
The parameter settings for our experiments are
given in section~\ref{sec:GAmvcp}.

@@

\State randomly select $V' = \{i_1, \dots, i_k\} \subseteq V = \{1, \dots, n\}$
\Comment{randomly select k different nodes}
\For

\end{algorithmic}
\end{algorit
For each of these graphs, a total of
$N = 100$ independent runs of the genetic algorithm is performed.
The results are summarized in table~\ref{fig:t1} for the best
fitness values that were encountered during the 100 runs.
For each problem instance, the different fitness values that were
obtained and their frequencies are recorded.
Furthermore, the average fitness value $\bar{f}$ over
all 100 runs is indicated at the bottom of the table.
For example, the first column in table~\ref{fig:t1} indicates
that the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 53$,
the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 54$,
the best obtained fitness value in 3 of the 100 runs was $f(\vec{x}) = 55$, and so on...
And the average of these values is indicated by $\bar{f}$, which is the average value of
the best obtained fitness values over the 100 runs.

@@

\subsection{expermental observations}

\section{Conclusion}
sit amet, consectetur adipisicing elit, sed do eiusmod

>>>>

% including packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{hyperref}
\usepackage{hypcap}
\usepackage[autostyle]{csquotes}
\usepackage[]{biblatex}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage[end]{algpseudocode}
\usepackage{caption}

@@

\section{Experimental Results}
\label{sec:er}
\setcounter{figure}{0}
\captionsetup[figure]{name={Table}}
For the experimental tests,
the genetic algorithm software package GENEsYs is used [1]misp.
This implementation is based on the widely used GENESIS software by Grefenstette
(see [3], pp. 374-377 misp), but allows for more 
flexibility concerning genetic operators and data monitoring.
The parameter settings for our experiments are
given in section~\ref{sec:GAmvcp}.

@@

\begin{algorithm}
\caption{Generate$(n, d, k)$}
\label{alg:gen}
\begin{algorithmic}[1]
\algnotext{EndFor}
\algnotext{EndIf}

\State randomly select $V' = \{i_1, \dots, i_k\} \subseteq V = \{1, \dots, n\}$
\State
\Comment{randomly select k different nodes, these nodes will hold a potential mvc}
\For{$i$}{$1$}{$n-1$}
\For{$j$}{$i+1$}{$n$}
\If{$(\text{Random(0, 1)} \leq d) \wedge (i \in V' \vee j \in V')$}
\State $e_{ij} = 1$
\Else
\State $e_{ij} = 0$
\EndIf
\EndFor
\EndFor

For each of these graphs, a total of
$N = 100$ independent runs of the genetic algorithm is performed.
The results are summarized in table~\ref{fig:t1} for the best
fitness values that were encountered during the 100 runs.
For each problem instance, the different fitness values that were
obtained and their frequencies are recorded.
Furthermore, the average fitness value $\bar{f}$ over
all 100 runs is indicated at the bottom of the table.
For example, the first column in table~\ref{fig:t1} indicates
that the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 53$,
the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 54$,
the best obtained fitness value in 3 of the 100 runs was $f(\vec{x}) = 55$, and so on...
And the average of these values is indicated by $\bar{f}$, which is the average value of
the best obtained fitness values over the 100 runs.

@@

\subsection{results comments}
From these tables, a number of interesting conclusions
can be drawn. For the random graphs used to compare the
genetic algorithm and the vercov algorithm,
it is known by construction that an optimum of quality 55 exists in the first test set,
(respectively, an optimum of quality 110 exists for the second test set). This optimum is likely to be the
global optimum, And it is found by the genetic
algorithm at least once within the $N = 100$ runs that were performed.

Moreover, the randomly constructed problems quickly
become simpler for the genetic algorithm when the edge
density is increased. For an edge density of $d \in \{0.4, 0.5\}$, the
genetic algorithm almost surely finds the global optimum
of the problems, while vercov algorithm gives a relatively terrible results.

In case of the regular graph after Papadimitriou and
Steiglitz, the genetic algorithm is able to find the global
optimum in about $2/3$ of all runs, while the remaining
runs identify a solution of quality $2k + 2$.
Whereas, vercov algorithm gives a solution of quality $2k + 2$ in all of the 100 runs as expected.
Recall that the graphs are constructed
so as to force the vercov algorithm into yielding solutions
of quality $2k + 2$.
The random choice of edges in line~\ref{alg:rand} of the algorithm implies that nodes from either layers one and two, or layers two and three are involved in the solution being constructed, which in turn implies that two layers have to be part of the solution found by the algorithm [10]mvcp.

For the randomly constructed graphs, the vercov algorithm performs
poorly.
It barely finds solutions of quality 80 (for graphs of size 100) and 172 (for graphs of size 200).
The average performance of the vercov algorithm (surprisingly)
decreases as the edge density is increased.
i.e. the problems become even harder for the vercov algorithm
while they become much simpler for the genetic algorithm when
the edge density increases.
The average fitness found by the genetic algorithm is notably
better than the one found by the vercov algorithm.
One can demonstrate this by calculating
the ratio of the absolute (or equivalently the relative) error.
For example, for the first problem instance,
let $\bar{f}_1, \bar{f}_2$ be the average found by
the genetic algorithm, vercov algorithm respectively.
We have $ (\bar{f}_2 - 55) / (\bar{f}_1 - 55) = (86.46 - 55)/(62.61 - 55) \approx 4 = 400\%$
that is, the error was reduced by a factor of 4.

\section{Conclusion}
In this work, we have demonstrated that genetic algorithms can be used in a straightforward way t
good approximate solutions of the minimum vertex cover
problem. Moreover, the results found by the genetic algorithm are better than those obtained from the best
known traditional heuristic, the vercov algorithm. These, in addition to other good results obtained on, highly constrained combinatorial optimization
problems such as the subset sum [7], minimum tardy
task [7], and multiple knapsack problems [8], give strong
evidence that genetic algorithms can yield good solutions for a wide range of hard combinatorial optimization problems for which solutions can be represented by
binary strings.
